\input{preamble}

\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }


\begin{document}
\title{Dwight D. Spencer - Manual}
\date{}
\maketitle
\vspace{-1cm}

\section*{Important rule}
DO NOT UNPLUG ANYTHING WHILE POWER IS TURNED ON OR DWIGHT WILL BE VERY SAD

\section*{Usage}
Select the game by pressing the \textbf{number buttons}.
During any game, press \textbf{left} and \textbf{right} simultaneously to go to game selection mode again.

\section*{Games}
\subsection*{1: Continuous Pouring}
Dwight will pour whenever \textbf{any button} is pressed. Super useful when instead of pouring things directly into your glass, you'd rather pour them into Dwight first, and then have Dwight do the hard work for you.

\subsection*{2: Shots}
Press \textbf{any number key}. Dwight will pour exactly as many shots as you the number you pressed.

\subsection*{3: Russian Roulette}
Everyone takes turns pressing \textbf{any button}.
A simple beep means you're fine. An annoying-ass melody means you lost. Put your glass under Dwight and then press \textbf{any button} to accept your fate.

\subsection*{4: The heroic battle for eternal glory fought with the sweat-forged weapon of reaction, where reaction is defined as the time it takes you to press a button after the beeping sound appears (be quick or be dead)}
The game is played in two teams of at most 3 players.
The left team uses buttons \textbf{1}, \textbf{4}, and \textbf{7}.
The right team uses buttons \textbf{3}, \textbf{6}, and \textbf{9}.
If there are fewer players in a team, the buttons with higher number are not required. 

To begin a round, all players press their corresponding \textbf{number button} simultaneously.
Let go of the button while the beautiful melody finishes playing.
If you keep your button pressed until after the melody finishes or press a button now, you LOSE! See the following section on the aftermath.

After a few seconds, Dwight will make a glorious beeping sound. Let the battle commence. The team that presses all their corresponding \textbf{number buttons} first, WINS! The other team LOSES!

\subsubsection*{Aftermath}
If you fought the battle properly, the LED of the losing team will blink. The team chooses who should drink. Put the glass under Dwight and press \textbf{any button} to let Dwight bless you with the glorious beverage of well-fought defeat.

However, if a team lost via an early start, Dwight will sing a beautiful ballad making fun of the player who started early. That player puts their glass under Dwight and receives the drink of shame by pressing \textbf{any button}.

\newpage
\subsection*{9: Configuration}
In the unlikely case that you are dissatisfied with Dwights services, this mode will help you configure away any problems you might have.
Press the \textbf{number key} for the variable you wish to change. Then type in the desired value using the \textbf{number keys} and confirm with the \textbf{right key}. Abort with the \textbf{left key}.

Variables:
\begin{enumerate}
  \item Time poured per shot in ms. Default value: 700 ms.
  \item Loss probability Russian Roulette in percent.
  \item Minimum number of shots for the loser of Russian Roulette.
  \item Maximum number of shots for the loser of Russian Roulette.
  \item Number of players for ``The heroic battle for eternal glory fought with the sweat-forged weapon of reaction, where reaction is defined as the time it takes you to press a button after the beeping sound appears.''.
  \item Number of shots for the losing team in the reaction battle.
  \item Number of shots for an early start in the reaction battle.
\end{enumerate}

Note: Configuration is lost when Dwight is turned off. That is just one of many reasons why Dwight should never be turned off.

\end{document}